Opportunities for improvement in the care of adult trauma patients arriving in shock

### 2024-11-30 thesis.Rmd
la till tabellen i metod på rätt plats
början av diskussionen

@@

-->
```
## Key results
We found that the most common type of OFI is Clinical judgement error across almost all shock severities and that there are minor if any association between shock severity and OFI.

>>>>

When doing the regression in steps, it can be observed that the biggest changes of OR occurs when adding the ISS parameter into the regression model both for the BE and SBP groups.

```{r Step log, echo=FALSE}
combined_table_stepBE
combined_table_stepSBP
```

@@

-->
```
## Key results
We found that the most common type of OFI is clinical judgement error across almost all shock severities. Out of all shock severities, there is only statistical significant association between severe shock with a BE of < -10 and OFI, which showes a 63% reduced odds of OFI when comparing against those with no shock.

Previous studies [@teixeira_preventable_2007] which studied cases with a deathly outcome, showed that the most common OFI type was delay in treatment (52,9%) while the second most common is clinical judgement error (21,6%). In comparison, our results showed the most common OFI is clinical judgement error (36%), while inadequate was second (22%) and delay in treatment comes third (17%). For patients defined as in shock, the most common was still clinical judgement error (35%).
